---
title: "eDNA pipeline summary"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    df_print: kable
params:
  report: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
report <- params$report
```

```{css echo=FALSE}
.report-highlight {
  display: inline;
  background-color: rgba(24, 188, 156, 0.35);
  color: inherit;
  padding: 0.05em 0.2em;
  border-radius: 0;
  box-decoration-break: clone;
  -webkit-box-decoration-break: clone;
}
.ampliseq-report-link {
  margin: 0 0 1.25rem;
}
```

<p class="ampliseq-report-link">
This pipeline builds on nf-core/ampliseq,
<a href="../../ampliseq/summary_report/summary_report.html" target="_blank">view the ampliseq summary report here</a>.
</p>

## Pipeline parameters

```{r parameters}
if (is.null(report$parameters)) {
  cat("No parameters file provided.\n")
} else {
  knitr::kable(report$parameters, col.names = c("Parameter", "Value"))
}
```

## ampliseq version

```{r revision}
if (!is.null(report$revision)) {
  knitr::kable(report$revision, col.names = c("Property", "Value"))
} else {
  cat(report$revision_message, "\n")
}
```

## Unmatched WoRMS names

ASVs with at least one rank assigned but no `scientificNameID`. Unique query names (finest filled rank):

<p><span class="report-highlight">`r report$unmatched_summary`</span></p>

```{r unmatched}
if (nrow(report$unmatched) == 0) {
  cat("None.\n")
} else {
  DT::datatable(
    report$unmatched,
    colnames = c("Name", "ASVs"),
    options = list(pageLength = 10, dom = "tip"),
    rownames = FALSE
  )
}
```

## SINTAX vs VSEARCH name agreement

<p><span class="report-highlight">`r report$sintax_species_changes`</span></p>

Per-rank comparison on shared ASV IDs.

```{r agreement}
knitr::kable(report$agreement)
```

## Final taxonomic annotation

```{r classification_rate, fig.width=7, fig.height=3.5}
if (is.null(report$classification_rate)) {
  cat("Occurrence table not available.\n")
} else {
  cr <- report$classification_rate
  par(mar = c(4, 6, 1, 1))
  bp <- barplot(
    cr$classified,
    names.arg = cr$rank,
    horiz = TRUE,
    las = 1,
    xlim = c(0, 100),
    xlab = "% ASVs classified",
    col = "#18BC9C",
    border = NA
  )
  text(cr$classified + 2, bp, labels = paste0(cr$classified, "%"), cex = 0.8, adj = 0)
}
```

```{r sunburst, fig.width=7, fig.height=7}
if (!is.null(report$sunburst)) {
  sb <- report$sunburst
  root_n <- sum(sb$n[sb$parent == ""])
  sb$parent[sb$parent == ""] <- "All"
  root <- data.frame(id = "All", label = "All", parent = "", n = root_n,
                     stringsAsFactors = FALSE)
  sb <- rbind(root, sb)
  plotly::plot_ly(
    type = "sunburst",
    ids = sb$id,
    labels = sb$label,
    parents = sb$parent,
    values = sb$n,
    branchvalues = "total",
    maxdepth = 4,
    insidetextorientation = "radial"
  )
}
```