---
title: "edna-pipelines summary report"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    df_print: kable
params:
  report: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
report <- params$report
```

```{css echo=FALSE}
.report-highlight {
  display: inline;
  background-color: rgba(24, 188, 156, 0.35);
  color: inherit;
  padding: 0.05em 0.2em;
  border-radius: 0;
  box-decoration-break: clone;
  -webkit-box-decoration-break: clone;
}
.ampliseq-report-link {
  margin: 0 0 1.25rem;
}
.report-meta {
  margin: 0 0 1rem;
  color: #555;
}
.tocify-extend-page {
  height: 0 !important;
}
```

<p class="report-meta">
Run date: `r report$run_date`, pipeline version: `r report$pipeline_version`.
</p>

<p class="ampliseq-report-link">
This pipeline builds on nf-core/ampliseq,
<a href="../../ampliseq/summary_report/summary_report.html" target="_blank">view the ampliseq summary report here</a>.
</p>

## Pipeline parameters

```{r parameters}
if (is.null(report$parameters)) {
  cat("No parameters file provided.\n")
} else {
  params_tbl <- report$parameters
  params_tbl <- params_tbl[!params_tbl$parameter %in% c("pipeline_version", "run_date"), , drop = FALSE]
  knitr::kable(params_tbl, col.names = c("Parameter", "Value"), row.names = FALSE)
}
```

## ampliseq version

```{r revision}
if (!is.null(report$revision)) {
  knitr::kable(report$revision, col.names = c("Property", "Value"))
} else {
  cat(report$revision_message, "\n")
}
```

## Unmatched WoRMS names

<p><span class="report-highlight">`r report$unmatched_summary`</span></p>

```{r unmatched}
if (nrow(report$unmatched) == 0) {
  cat("None.\n")
} else {
  DT::datatable(
    report$unmatched,
    colnames = c("Name", "ASVs"),
    options = list(pageLength = 10, dom = "tip"),
    rownames = FALSE
  )
}
```

## SINTAX vs VSEARCH name agreement

<p><span class="report-highlight">`r report$sintax_species_changes`</span></p>

```{r agreement}
knitr::kable(report$agreement)
```

## Final taxonomic annotation

```{r classification_rate, fig.width=7, fig.height=3.5}
if (is.null(report$classification_rate)) {
  cat("Occurrence table not available.\n")
} else {
  cr <- report$classification_rate
  par(mar = c(4, 6, 1, 1))
  bp <- barplot(
    cr$classified,
    names.arg = cr$rank,
    horiz = TRUE,
    las = 1,
    xlim = c(0, 100),
    xlab = "% ASVs classified",
    col = "#18BC9C",
    border = NA
  )
  text(cr$classified + 2, bp, labels = paste0(cr$classified, "%"), cex = 0.8, adj = 0)
}
```

```{r sunburst, fig.width=7, fig.height=7}
if (!is.null(report$sunburst)) {
  sb <- report$sunburst
  root_n <- sum(sb$n[sb$parent == ""])
  sb$parent[sb$parent == ""] <- "All"
  root <- data.frame(id = "All", label = "All", parent = "", n = root_n,
                     stringsAsFactors = FALSE)
  sb <- rbind(root, sb)
  sb$depth <- ifelse(sb$id == "All", 0L, lengths(strsplit(sb$id, " - ", fixed = TRUE)))
  teal_shades <- c("#E8F8F5", "#A3E4D7", "#52BEA0", "#18BC9C", "#148F77", "#0E6655", "#0B5345")
  sb$color <- teal_shades[pmin(sb$depth + 1L, length(teal_shades))]
  plotly::plot_ly(
    type = "sunburst",
    ids = sb$id,
    labels = sb$label,
    parents = sb$parent,
    values = sb$n,
    branchvalues = "total",
    maxdepth = 4,
    insidetextorientation = "radial",
    marker = list(colors = sb$color, line = list(color = "white", width = 1))
  )
}
```

## Detected species

Species-level assignments in the final occurrence table.

```{r detected_species}
if (is.null(report$detected_species)) {
  cat("Occurrence table not available.\n")
} else if (nrow(report$detected_species) == 0) {
  cat("None.\n")
} else {
  DT::datatable(
    report$detected_species,
    colnames = c("Species", "Phylum", "Class", "ASVs", "Reads", "Samples"),
    options = list(pageLength = 15, dom = "tip", order = list(list(4, "desc"))),
    rownames = FALSE
  )
}
```