---
title: "eDNA pipeline summary"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: false
    df_print: kable
params:
  report: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
report <- params$report
```

```{css echo=FALSE}
.report-highlight {
  display: inline;
  background-color: rgba(24, 188, 156, 0.35);
  color: inherit;
  padding: 0.05em 0.2em;
  border-radius: 0;
  box-decoration-break: clone;
  -webkit-box-decoration-break: clone;
}
.ampliseq-report-link {
  margin: 0 0 1.25rem;
}
```

<p class="ampliseq-report-link">
This pipeline builds on nf-core/ampliseq,
<a href="../../ampliseq/summary_report/summary_report.html" target="_blank">view the ampliseq summary report here</a>.
</p>

## Pipeline parameters

```{r parameters}
if (is.null(report$parameters)) {
  cat("No parameters file provided.\n")
} else {
  knitr::kable(report$parameters, col.names = c("Parameter", "Value"))
}
```

## ampliseq version

```{r revision}
if (!is.null(report$revision)) {
  knitr::kable(report$revision, col.names = c("Property", "Value"))
} else {
  cat(report$revision_message, "\n")
}
```

## Unmatched WoRMS names

ASVs with at least one rank assigned but no `scientificNameID`. Unique query names (finest filled rank):

<p><span class="report-highlight">`r report$unmatched_summary`</span></p>

```{r unmatched}
if (nrow(report$unmatched) == 0) {
  cat("None.\n")
} else {
  DT::datatable(
    report$unmatched,
    colnames = c("Name", "ASVs"),
    options = list(pageLength = 10, dom = "tip"),
    rownames = FALSE
  )
}
```

## SINTAX vs VSEARCH name agreement

<p><span class="report-highlight">`r report$sintax_species_changes`</span></p>

Per-rank comparison on shared ASV IDs.

```{r agreement}
knitr::kable(report$agreement)
```
